### 2011-12-11 plos_template.tex
small change
minor work on technical methods

\section*{Introduction}
Genome Wide Association Studies (GWAS) are an easy and cheap way to find Single Nucleotide Polymorphisms (SNPs) which can be interesting because of their medical relevance. SNPs found through GWAS can be used to find candidate genes for a closer inspection or to predict disease risks. Genome Wide Association Studies make use of statistics to compare the alleles of patients to the alleles of healthy controls. By this the method does not allow to find causal differences but mere correlations. The first GWAS was published in 2005 and compared age-related macular degeneration in contrast to a healthy control group (doi:10.1126/science.1109557). Since the beginning the number of participants in those studies is rising and over 1200 GWAS have been performed (doi:10.1186/1471-2350-10-6.) and over 5000 SNPs have been linked to different diseases and traits in those studies %(http://www.genome.gov/page.cfm?pageid=26525384&clearquery=1#result_table).

@@

\subsection*{Technical realization of the platform}
The main platform is realized using the web-framework Ruby on Rails. Postgres is used as the main database backend for Rails. The database stores genotyping results, phenotypic information of the users, literature results of Mendeley, the Public Library of Science and summaries on SNPs which can be found in SNPedia.

The literature database of Mendeley is queried using the REST API, which delivers results in JSON. The literature database of the Public Library of Science is queried using the respective REST API, which delivers results in XML. Summaries on SNPs are provided by SNPedia, through querying the content through the MediaWiki-API.

>>>>

\section*{Introduction}
Genome Wide Association Studies (GWAS) are an easy and cheap way to find Single Nucleotide Polymorphisms (SNPs) which can be interesting because of their medical relevance. SNPs found through GWAS can be used to find candidate genes for a closer inspection or to predict disease risks. Genome Wide Association Studies make use of statistics to compare the alleles of patients to the alleles of healthy controls. By this the method it is not possbile to find causal differences but mere correlations. The first GWAS was published in 2005 and compared age-related macular degeneration in contrast to a healthy control group (doi:10.1126/science.1109557). Since the beginning the number of participants in those studies is rising and over 1200 GWAS have been performed (doi:10.1186/1471-2350-10-6.) and over 5000 SNPs have been linked to different diseases and traits in those studies %(http://www.genome.gov/page.cfm?pageid=26525384&clearquery=1#result_table).

@@

\subsection*{Technical realization of the platform}
The main platform is realized using the web-framework Ruby on Rails. Postgres is used as the main database backend for Rails. The database stores genotyping results, phenotypic information of the users, literature results of Mendeley, the Public Library of Science and summaries on SNPs which can be found in SNPedia. The literature database of Mendeley is queried using the REST API, which delivers results in JSON. The literature database of the Public Library of Science is queried using the respective REST API, which delivers results in XML. Summaries on SNPs are provided by SNPedia, through querying the content through the MediaWiki-API.

SNPs are cataloged by their unique identifier, which consists of a prefix (mostly \textit{rs}) and a unique number. This is a common format which is used by the NCBI dbSNP database and is also widely used and easily parsed from different literature-sources.
